WED-SQL (Draft)

### 2016-06-21 doc/paper/main_en.tex
final abstract

\begin{abstract}
%\boldmath
%\blindtext[1]
Business process models designed and implemented under WED-flow concepts are true dynamic systems, easy to evolve in a
incremental and adaptive approach and drastically reducing the complexity of exceptions handling when compared to other
more traditional frameworks (like BPEL, Process Algebra and Petri Networks). On the implementation side, however, these
systems must either provide an extra software layer or use some external toolkit, or even a framework, to be able to enforce 
a data-state based transaction control, what includes dealing with semantic exceptions. In this paper we present the 
WED-SQL, a distributed framework that provides a reliable e efficient way to write and implement WED-flow applications.
One of its main attributes is the integration with the PostgreSQL Relational Database Management System, which enables
the WED-SQL to take full advantage of all the transactional properties provided and also benefit from the SQL language
to specify the WED-flow definitions (e.g. WED-conditions, WED-transitions, and so on).

>>>>

\begin{abstract}
Despite the significant evolution of the design and implementation of business process models, a transactional approach 
that evolves an incremental and adaptive strategy remains an important challenge to be overcome for database management 
systems. Traditional frameworks such as BPEL, Process Algebra, and Petri Net require an additional  software layer or some 
external toolkits to be able to enforce a data-state based transaction control and deal with semantic exceptions. However, 
the complexity of implementation based on these traditional frameworks, especially to treat exceptions, is too high. In 
this paper, we present the WED-SQL, a distributed framework that provides a reliable and efficient way to design  and 
implement business processes. Our main contribution is the integration of WED-flow concepts into the PostgresSQL RDBMS. 
This integration enables the WED-SQL to take full advantage of  transactional properties and also benefit from the SQL 
language to specify the WED-flow definitions.
\end{abstract}

%\begin{abstract}
%\boldmath
%\blindtext[1]
%Business process models designed and implemented under WED-flow concepts are true dynamic systems, easy to evolve in a
%incremental and adaptive approach and drastically reducing the complexity of exceptions handling when compared to other
%more traditional frameworks (like BPEL, Process Algebra and Petri Networks). On the implementation side, however, these
%systems must either provide an extra software layer or use some external toolkit, or even a framework, to be able to enforce 
%a data-state based transaction control, what includes dealing with semantic exceptions. In this paper we present the 
%WED-SQL, a distributed framework that provides a reliable e efficient way to write and implement WED-flow applications.
%One of its main attributes is the integration with the PostgreSQL Relational Database Management System, which enables
%the WED-SQL to take full advantage of all the transactional properties provided and also benefit from the SQL language
%to specify the WED-flow definitions (e.g. WED-conditions, WED-transitions, and so on).
